The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2022-09-06 src/tex/ms.tex
changed to Z per Zsun

%%%%%%%%%%%%%%%
\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-1590-8551]{C. Conroy}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0003-3308-2420]{R. Pakmor}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{L. Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract 
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts, while also revealing new features in source property distributions.
To interpret these observations, we need to compare them to predictions from stellar population models. Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function.%and understanding its behaviour is essential to explain simulation results. 
In this work, we propose a simple analytical function for \SFRDzZ. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. 
%Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are: I) the locations of features are remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
% We further find that: III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution. 
% IV) the shape of the overall star-formation rate density has a small impact on the local mass distribution.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%opening from Chruslinska & Nelemans. Crucially needed are simple prescriptions
% 2 ways in which we can tackle this: observationally or theoretically
% 3 problemen met waarnemingen: 1) high redshift cant see, 2) metallicity measurements 3) xx?
% Theoretical: issues with illustris 1, here we provide a simple  fit to 
% give zenodo + data
% dan een beetje science 
% Er zijn allemaal BBH detecties, super leuk
% Om de rate te bedenken moeten we niet alleen numbe of meging BBH maar ook SFRD
% In dit paper geven we een nieuwe SFRD fit

% Er zijn vechillende manieren om een SFRD meer te geven

@@

% combines a  with an approximation of the metallicity distribution that
The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}. However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}. Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.

% \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
One can also directly extract the metallicity-dependent cosmic star formation history from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2022_rates}. However, these simulations currently lack the resolution to resolve the lowest mass galaxies, and their variations in \SFRDzZ span a smaller range than those observed in observationally-based models \citep{Pakmor+2022}.

@@

%Arguments: cosmological simulations work at high z,  but are they real? observations 
In this work we follow the latter approach and propose a flexible analytical model for \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. 
In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails.

The purpose of this proposed form is twofold.  
First of all, the form we propose allows for an intuitive interpretation of the free parameters. This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in Section \ref{sec: mass dists} using GW predictions as an example). By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties can be systematically explored.
%
Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of \SFRDzZ that can be easily updated when new information becomes available. % which is the motivation for this work. 
In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift
metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations. 
% we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients. Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations.

% is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients. By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.

@@

Throughout this work, we adopt a universal Kroupa initial mass function \citep{Kroupa2001} with the mass
limits $0.01–200\Msun$ and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.

@@

%% SFR(z) %%

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The cosmic metallicity density distribution}
For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

The skewed-log-normal distribution of metallicities is defined as:
% See eq. 1 here: https://www.emis.de/journals/RCE/V36/v36n1a03.pdf
\begin{equation}
\begin{aligned}
\label{eq: pure log skew}
\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
&= \frac{1}{Z} \times \frac{2}{\omega}
    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
                 }_{(a)}
    \underbrace {
                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
                }_{(b)},
\end{aligned}
\end{equation}

\noindent where (a) is the standard log-normal distribution, $\phi$,
%
\begin{equation}
\label{eq: log normal and CDF}
 \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
% \underbrace{
    \frac{1}{\sqrt{2 \pi}} 
    \exp{
         \left\{
            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
        \right\}
        }
  %  }_{(1)} 
    \end{equation}
and (b) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
    \begin{equation}
    \begin{array}{cc}
 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
    \frac{1}{2} 
    \left[ 
        1 + {\rm erf}
            \left\{
                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
            \right\} 
    \right] . \\
    \end{array}
\end{equation}

@@

For the evolution of the mean metallicity with redshift we follow \cite{LangerNorman2006} and the phenomenological model from \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
\begin{equation}
\label{eq: mean Z}
    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
\end{equation}
where $\mu_0
%= 0.025 
$ is the mean metallicity at redshift 0, and $\mu_z
%= -0.048
$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,

% \begin{equation}
% \label{eq mu z}
%     \xi(z) = -\frac{\omega^2}{2}\, \ln\left(\frac{  \mu_0 \cdot 10^{\mu_z \cdot z} }{2\, \Phi(\beta\, \omega)}  \right).
% \end{equation}

@@

We will also allow the ``scale'' $\omega$ to evolve with redshift in a similar manner, 
\begin{equation}
\label{eq: omega z}
    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
\end{equation}
where $\omega_0$ is
%$\omega_0 = 1.125$, 
the width of the metallicity distribution at $z=0$, and $\omega_z$
%$\omega_z = 0.048$, 
the redshift evolution of the scale.

@@

%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \omega_0 = 1.125, \omega_z = 0.048$ and $\alpha = -1.77$.

@@

% \subsection{Combined function}
Lastly, we combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific star formation rate density as described in equation \ref{eq: total sfrd}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations. The top panel shows the full two dimensional \SFRDzZ linear in time. Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. 
The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom channel). We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines. The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star-formation rate density.
Below we briefly discuss the IllustrisTNG simulations, and elaborate on our fitting procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IllustrisTNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. 
% In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift% metallicity studies in previously unexplored regimes \citep[e.g.,][]{Sanders+2022}.
%
Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

The IllustrisTNG-project (or TNG in short) considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations \citep[][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018, Nelson2019a, Pillepich2019}.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
% Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.

The models implemented in the publicly available TNG simulations \citep{Nelson2019b}\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. 
These models where calibrated at the resolution of the TNG100 simulation, hence TNG100 is expected to provide the best overall agreement to global properties (like the star formation rate density). This is why we adopt the TNG100 simulation as our fiducial simulation.
%
For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations, we refer to \cite{Pakmor+2022}. In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}, using an effective equation of state \citep{SpringelHernquist2003}. The stellar metallicity yields are an updated version of the original Illustris simulations as described in \cite{Pillepich2018}. Star particles deposit metals into the gas through type Ia and type II supernovae, as well as through asymptotic giant branch stars. 
% Positives on TNG
The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018}, metallicity gradients within galaxies at low redshift \citep{Hemler+2021}, and the reduction of star formation in the centers of star-forming galaxies \citep{Nelson2021}. %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}   
Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2022_rates,Bavera+2022,vanson+2022}. 
Out of the four \SFRDzZ variations explored, \cite{Briel+2022_rates} find that TNG provides one of the best agreements between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients, when combined with their fiducial binary population synthesis model. 
% TNG50 has higher res, but that also leads to higher stellar masses at fixed halo mass."

@@

We first consider a given redshift $z_j$.  For this redshift we compute the sum of the squared residuals between the cosmological simulation and our fit. This is effectively the square of the $l^2$-norm:
%
\begin{equation}
\label{eq: chisquare}
    \chi^2 (z_j) \equiv \sum_{Z_i} \left( 
        \mathcal{S}(Z_i,z_j)_{\rm sim} - 
        \mathcal{S}(Z_i,z_j)_{\rm fit}\right)^2 .
    %chi_square = ((obs - model )**2)/np.sum(model) 
\end{equation}
%
Here, the variable $Z_i$ runs over all metallicity bins.
%, but excludes bins where the star formation rate density is lower $10^{-10} \Msun \yr \Mpc^{-3}$ per bin. 
% Subsequently we sum the $\chi^2 (z_j)$ for all redshift bins $z_j$. 
We are particularly interested in properly fitting the low metallicity star formation at high redshifts. At high redshifts, the overall star-formation rate density is generally lower. To ensure that our fitting procedure gives sufficient weight to the behaviour at all redshifts, we introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight at redshifts where the overall star-formation rate density is lower.  To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.  Our final expression for the cost function reads

\begin{equation}
\label{eq: cost function}
    \chi  = \sum_{z_j} \frac{ \chi^2 (z_j) } 
        {\sum_{Z_i} \mathcal{S}(Z_i,z_j)}
    %chi_square = ((obs - model )**2)/np.sum(model) 
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model. 
% With the fit parameters as mentioned above, we find a maximum residual between the model and the TNG100 data of $2.3\cdot 10^{-3} \Msun \yr^{-1} \Mpc^{-3}$ at any given redshift.

@@

The flexibility of the model presented in this work can capture the large uncertainties that remain in the shape and normalisation of the metallicity-dependent cosmic star formation history. 
Our hope is that this expression will provide a useful starting point for making predictions and comparisons with observations.
% As such, we anticipate that it will be a helpful tool in other works that present \SFRDzZ dependent rates.

>>>>

%%%%%%%%%%%%%%%
\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-1590-8551]{C. Conroy}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0003-3308-2420]{R. Pakmor}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0001-6950-1629]{L. Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract 
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts, while also revealing new features in source property distributions.
To interpret these observations, we need to compare them to predictions from stellar population models. Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function.
In this work, we propose a simple analytical function for \SFRDzZ. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. 
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are: I) the locations of features are remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
\end{abstract}

@@

The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}. However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}. Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.

One can also directly extract the metallicity-dependent cosmic star formation history from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2022_rates}. However, these simulations currently lack the resolution to resolve the lowest mass galaxies, and their variations in \SFRDzZ span a smaller range than those observed in observationally-based models \citep{Pakmor+2022}.

@@

In this work we follow the latter approach and propose a flexible analytical model for \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. 
In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails.

The purpose of this proposed form is twofold.  
First of all, the form we propose allows for an intuitive interpretation of the free parameters. This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in Section \ref{sec: mass dists} using GW predictions as an example). By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties can be systematically explored.
%
Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of \SFRDzZ that can be easily updated when new information becomes available. 
In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift
metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations.

@@

Throughout this work, we adopt a universal Kroupa initial mass function \citep{Kroupa2001} with the mass
limits $0.01 - 200\Msun$ and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.

@@

%% SFR(z) %%
\subsection{The cosmic metallicity density distribution}
For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

The skewed-log-normal distribution of metallicities is defined as:
\begin{equation}
\begin{aligned}
\label{eq: pure log skew}
\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
&= \frac{1}{Z} \times \frac{2}{\omega}
    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
                 }_{(a)}
    \underbrace {
                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
                }_{(b)},
\end{aligned}
\end{equation}

\noindent where (a) is the standard log-normal distribution, $\phi$,
%
\begin{equation}
\label{eq: log normal and CDF}
 \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
    \frac{1}{\sqrt{2 \pi}} 
    \exp{
         \left\{
            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
        \right\}
        }
    \end{equation}
and (b) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
    \begin{equation}
    \begin{array}{cc}
 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
    \frac{1}{2} 
    \left[ 
        1 + {\rm erf}
            \left\{
                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
            \right\} 
    \right] . \\
    \end{array}
\end{equation}

@@

For the evolution of the mean metallicity with redshift we follow \cite{LangerNorman2006} and the phenomenological model from \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
\begin{equation}
\label{eq: mean Z}
    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
\end{equation}
where $\mu_0
$ is the mean metallicity at redshift 0, and $\mu_z
$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,

@@

We will also allow the ``scale'' $\omega$ to evolve with redshift in a similar manner, 
\begin{equation}
\label{eq: omega z}
    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
\end{equation}
where $\omega_0$ is
the width of the metallicity distribution at $z=0$, and $\omega_z$
the redshift evolution of the scale.

@@

@@

Lastly, we combine equations \ref{eq: z log skew} and \ref{eq: sfr1} to form a full metallicity specific star formation rate density as described in equation \ref{eq: total sfrd}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations. The top panel shows the full two dimensional \SFRDzZ linear in time. Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. 
The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom panel). We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines. The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star-formation rate density.
Below we briefly discuss the IllustrisTNG simulations, and elaborate on our fitting procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IllustrisTNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

The IllustrisTNG-project (or TNG in short) considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations \citep[][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018, Nelson2019a, Pillepich2019}.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.

The models implemented in the publicly available TNG simulations \citep{Nelson2019b}\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. 
These models where calibrated at the resolution of the TNG100 simulation, hence TNG100 is expected to provide the best overall agreement to global properties (like the star formation rate density). This is why we adopt the TNG100 simulation as our fiducial simulation.
%
For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations, we refer to \cite{Pakmor+2022}. In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}, using an effective equation of state \citep{SpringelHernquist2003}. The stellar metallicity yields are an updated version of the original Illustris simulations as described in \cite{Pillepich2018}. Star particles deposit metals into the gas through type Ia and type II supernovae, as well as through asymptotic giant branch stars. 
% Positives on TNG
The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018}, metallicity gradients within galaxies at low redshift \citep{Hemler+2021}, and the reduction of star formation in the centers of star-forming galaxies \citep{Nelson2021}. 
Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2022_rates,Bavera+2022,vanson+2022}. 
Out of the four \SFRDzZ variations explored, \cite{Briel+2022_rates} find that TNG provides one of the best agreements between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients, when combined with their fiducial binary population synthesis model.

@@

We first consider a given redshift $z_j$.  For this redshift we compute the sum of the squared residuals between the cosmological simulation and our fit. This is effectively the square of the $l^2$-norm:
%
\begin{equation}
\label{eq: chisquare}
    \chi^2 (z_j) \equiv \sum_{Z_i} \left( 
        \mathcal{S}(Z_i,z_j)_{\rm sim} - 
        \mathcal{S}(Z_i,z_j)_{\rm fit}\right)^2 .
    %chi_square = ((obs - model )**2)/np.sum(model) 
\end{equation}
%
Here, the variable $Z_i$ runs over all metallicity bins.
We are particularly interested in properly fitting the low metallicity star formation at high redshifts. At high redshifts, the overall star-formation rate density is generally lower. To ensure that our fitting procedure gives sufficient weight to the behaviour at all redshifts, we introduce a penalisation factor to somewhat reduce the contribution of redshifts where the peak of cosmic star formation occurs, while increasing the weight at redshifts where the overall star-formation rate density is lower.  To achieve this we divide $\chi^2 (z_j)$ by the star formation $\sum_{Z_i} \mathcal{S}(Z_i,z_j)$ per redshift bin before adding the contribution of all redshifts.  Our final expression for the cost function reads

\begin{equation}
\label{eq: cost function}
    \chi  = \sum_{z_j} \frac{ \chi^2 (z_j) } 
        {\sum_{Z_i} \mathcal{S}(Z_i,z_j)}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.

@@

The flexibility of the model presented in this work can capture the large uncertainties that remain in the shape and normalisation of the metallicity-dependent cosmic star formation history. 
Our hope is that this expression will provide a useful starting point for making predictions and comparisons with observations.
